Optimal (Multiway) Spatial Joins

### 2024-06-02 msj.tex

\extraspacing \noindent {\bf Proof of Lemma~\ref{lmm:hv:type2:recur-output}.} Before proving the lemma, let us prove a fact that will be useful later: the set $\contained_{R_{k-2}}(\bm{t})$ is non-empty for each tuple $\bm{t} \in \J(R_1,...,R_{k-3},H',V)$. Let $h$ be the full segment of $\bm{t}[k-2]$. By the definition of a trimmed segment, there exists a rectangle $r_{k-2} \in R_{k-2}$ that covers both endpoints of $h$. Thus, the effective horizontal segment of $\bm{t}$, which is contained in $h'$, must also covered by $r_{k-2}$. This implies that $\cross_{R_{k-2}}(\bm{t})$ cannot be empty (as it includes at least $r_{k-2}$).

@@

\extraspacing \underline{\em Proof of Statement (1).} We will map each segment $h^* \in H^*$ to a unique tuple $\bm{t}\in \J(R_1,...,R_{k-3},H',V)$ satisfying $\cross_{R_{k-2}}(\bm{t}) = \cross_{R_{k-2}}(h^*)$. We can then derive that
\myeqn{
    \sum_{h^* \in H^*} |\cross_{R_{k-2}}(h^*)| \le \sum_{\bm{t} \in \J(R_1,...,R_{k-3},H',V)} |\cross_{R_{k-2}}(\bm{t})| \leq \out, \nn
} where the last inequality is due to Statement (3) of Lemma~\ref{lmm:hv:type2:properties}.

@@

Next, we will prove that a rectangle $r_{k-2} \in \cross_{R_{k-2}}(h^*)$ if and only if $r_{k-2} \in \cross_{R_{k-2}}(\bm{t})$. According to the definitions of $\cross_{R_{k-2}}(h^*)$ and $\cross_{R_{k-2}}(\bm{t})$ --- see \eqref{eqn:contained} and \eqref{eqn:type2:contained-t}, respectively --- it suffices to show that $h^*$ is the same as the effective horizontal segment of $\bm{t}$. Denote by $x$ the x-coordinate of the vertical segment $\bm{t}[k-1]$. Then, the point $h' \cap v$ (intersection between $h'$ and $v$) is $(x,y)$, where as mentioned $y$ is the y-coordinate of $h'$. The effective horizontal segment of $\bm{t}$ is therefore $[x_1,x]\times y$. Recall that $h^* = [x_1,\minleft(h')]\times y$, where $\minleft(h') = \text{$x$-coordinate of $\bm{t}[k-1]$} = x$. Therefore, $h^*$ is the same as the effective horizontal segment of $\bm{t}$.

@@

Firstly, we will prove $\contained_{R_{k-2}}(\bm{t})\subseteq \cross_{R_{k-2}}(h^*)$. For this purpose, we will show that any rectangle $r_{k-2} \in \contained_{R_{k-2}}(\bm{t})$ also covers $h^*$. It suffices to show that $h^*$ is contained in the effective horizontal segment of $\bm{t}$. Combining the definition of $\minleft(h')$ (see \eqref{eqn:minleft}), and the fact that $x$ is the x-coordinate of $\bm{t}[k-1]$, we have $\minleft(h') \le x$. This implies that $h^* = [x_1, \minleft(h')] \times y$ is contained in $[x_1, x] \times y$, i.e. the effective horizontal segment of $\bm{t}$.

>>>>

\extraspacing \noindent {\bf Proof of Lemma~\ref{lmm:hv:type2:recur-output}.} Before proving the lemma, let us prove a fact that will be useful later: the set $\contained_{R_{k-2}}(\bm{t})$ is non-empty for each tuple $\bm{t} \in \J(R_1,...,R_{k-3},H',V)$. Let $h$ be the full segment of $\bm{t}[k-2]$. By the definition of a trimmed segment, there exists a rectangle $r_{k-2} \in R_{k-2}$ that covers both endpoints of $h$. Thus, the effective horizontal segment of $\bm{t}$, which is contained in $h'$, must also covered by $r_{k-2}$. This implies that $\contained_{R_{k-2}}(\bm{t})$ cannot be empty (as it includes at least $r_{k-2}$).

@@

\extraspacing \underline{\em Proof of Statement (1).} We will map each segment $h^* \in H^*$ to a unique tuple $\bm{t}\in \J(R_1,...,R_{k-3},H',V)$ satisfying $\contained_{R_{k-2}}(\bm{t}) = \contained_{R_{k-2}}(h^*)$. We can then derive that
\myeqn{
    \sum_{h^* \in H^*} |\contained_{R_{k-2}}(h^*)| 
    &\le& \sum_{\bm{t} \in \J(R_1,...,R_{k-3},H',V)} |\contained_{R_{k-2}}(\bm{t})| \nn \\
    &\leq& \out, \nn
} where the last inequality is due to Statement (3) of Lemma~\ref{lmm:hv:type2:properties}.

@@

Next, we will prove that a rectangle $r_{k-2} \in \contained_{R_{k-2}}(h^*)$ if and only if $r_{k-2} \in \contained_{R_{k-2}}(\bm{t})$. According to the definitions of $\contained_{R_{k-2}}(h^*)$ and $\contained_{R_{k-2}}(\bm{t})$ --- see \eqref{eqn:contained} and \eqref{eqn:type2:contained-t}, respectively --- it suffices to show that $h^*$ is the same as the effective horizontal segment of $\bm{t}$. Denote by $x$ the x-coordinate of the vertical segment $\bm{t}[k-1]$. Then, the point $h' \cap v$ (intersection between $h'$ and $v$) is $(x,y)$, where as mentioned $y$ is the y-coordinate of $h'$. The effective horizontal segment of $\bm{t}$ is therefore $[x_1,x]\times y$. Recall that $h^* = [x_1,\minleft(h')]\times y$, where $\minleft(h') = \text{$x$-coordinate of $\bm{t}[k-1]$} = x$. Therefore, $h^*$ is the same as the effective horizontal segment of $\bm{t}$.

@@

Firstly, we will prove $\contained_{R_{k-2}}(\bm{t})\subseteq \contained_{R_{k-2}}(h^*)$. For this purpose, we will show that any rectangle $r_{k-2} \in \contained_{R_{k-2}}(\bm{t})$ also covers $h^*$. It suffices to show that $h^*$ is contained in the effective horizontal segment of $\bm{t}$. Combining the definition of $\minleft(h')$ (see \eqref{eqn:minleft}), and the fact that $x$ is the x-coordinate of $\bm{t}[k-1]$, we have $\minleft(h') \le x$. This implies that $h^* = [x_1, \minleft(h')] \times y$ is contained in $[x_1, x] \times y$, i.e. the effective horizontal segment of $\bm{t}$.
